Implicit yaddayadda

### 2011-09-27 papers/PLDI2012/implicitization.tex
typos

\subsection{Guided static analysis}
\label{sec:guided}
\emph{Guided static analysis} was proposed by \citet{DBLP:conf/sas/GopanR07} as an improved over classical upward Kleene iterations with widening.
Consider the following program:
\lstinputlisting{gopan_reps.c}

@@

The set of paths is kept implicit by an SMT formula $\rho$ expressing
the semantics of the program, assuming that the transition semantics can be
expressed within a decidable theory. For an easy construction of $\rho$, 
we also assume that the program in expressed in SSA form, meaning that each
variable is only assigned once in the transition graph. This is not a
restriction, since there exist standard algorithms that transform a program into
an SSA format.

>>>>

\subsection{Guided static analysis}
\label{sec:guided}
\emph{Guided static analysis} was proposed by \citet{DBLP:conf/sas/GopanR07} as an improvement over classical upward Kleene iterations with widening.
Consider the following program:
\lstinputlisting{gopan_reps.c}

@@

The set of paths is kept implicit by an SMT formula $\rho$ expressing
the semantics of the program, assuming that the transition semantics can be
expressed within a decidable theory. For an easy construction of $\rho$, 
we also assume that the program is expressed in SSA form, meaning that each
variable is only assigned once in the transition graph. This is not a
restriction, since there exist standard algorithms that transform a program into
an SSA format.
